European or American? A re-examination of the transatlantic influence over the IMF

### 2025-04-22 demo/demo.qmd
demo: disable package installation

```{r setup}
need <- c('tidyverse','haven','AER','fixest','modelsummary',
          'corrplot', 'kableExtra','car','parameters') # list packages needed
have <- need %in% rownames(installed.packages()) # checks packages you have
if(any(!have)) install.packages(need[!have]) # install missing packages
invisible(lapply(need, library, character.only=T))
```

>>>>

```{r setup}
need <- c('tidyverse','haven','AER','fixest','modelsummary',
          'corrplot', 'kableExtra','car','parameters') # list packages needed
# have <- need %in% rownames(installed.packages()) # checks packages you have
# if(any(!have)) install.packages(need[!have]) # install missing packages
invisible(lapply(need, library, character.only=T))
```
